%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Dinesh}{Adepu}
\email{adepu.dinesh.a@gmail.com}
\phone[mobile]{+91 9963943672}
\address{11-29-106, 2nd Bank Colony, Warangal, India}


\begin{document}

\recipient{To}{The Project Incharge, \\
               GFZ, Helmholtz centre of geosciences,\\
               Germany}
\date{\today}
\opening{\textbf{Sub: Application for the post of Postdoctoral researcher – Coupling of research software to model solid Earth processes.}}
% with reference advertisement: XXXX/XX, dated 04-03-2022
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear team,
\\
%references such as what and how you got this information
\vspace{1em}
I am Dinesh Adepu, and I hold an M.Tech and Ph.D. in Aerospace
Engineering from IIT Bombay, followed by a postdoctoral fellowship in
the Chemical Engineering Department at the University of
Surrey. Currently, I am working as a postdoctoral researcher at IIT
Delhi, India. \\


\vspace{1em}
 During my Ph.D., I developed a novel numerical technique
in Smoothed Particle Hydrodynamics (SPH) to study fluid and elastic
dynamics.  Further, the developed method is coupled with the discrete
element method (DEM) to handle the rigid-fluid coupling, where ocean
engineering problems are handled. As a multiphysics application, the
developed technique is applied to model the fluid-structure
interaction phenomenon. All the above work is implemented in PySPH and
is fully open-source and reproducible. I have developed a parallel
n-body software in memory-safe Rust programming language, in which DEM
is implemented. \\


\vspace{1em}
As a postdoctoral researcher at the University of Surrey, I
contributed to an EPSRC-funded project studying particle dispersion,
swelling, and agglomeration in stirring tanks using an SPH-DEM
solver. This project led to the development of an open-source solver
integrated with PySPH and DEM. To address large-scale mixing
challenges, I also created an exascale-capable DEM solver using the
Cabana framework, built on C++ and leveraging Kokkos for heterogeneous
computing. I am currently using FEM to model dendrite growth in Li-ion batteries.\\


\vspace{1em}
With my demonstrated expertise in numerical modeling, high-performance
computing, and large-scale code development, I am confident in my
ability to contribute effectively to the proposed position. My proven
track record in tackling complex computational challenges in these
areas will bring significant value to the institution and play a
meaningful role in the success of the project.\\



\vspace{1em}
Thank you for considering my application. I look forward to the
opportunity to discuss my qualifications further.\\

% Sincerely,


\vspace{0.5cm}


\makeletterclosing

\end{document}
