%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Dinesh}{Adepu}
\email{adepu.dinesh.a@gmail.com}
\phone[mobile]{+91 9963943672}
\address{A-712, H13, IIT Bombay, Bombay, India}


\begin{document}

\recipient{To}{The Project Incharge, \\
               College of Design and Engineering,\\
               Kent Ridge Campus,\\
               Department of Mechanical Engineering,\\
               NUS, Singapore}
\date{\today}
\opening{\textbf{Sub: Application for the post of Research Fellow (Computation).}}
% with reference advertisement: XXXX/XX, dated 04-03-2022
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear Sir,
\\
%references such as what and how you got this information
\vspace{1em} I am Dinesh Adepu, currently in my M.Tech+Ph.D. program in the
Aerospace Engineering department at IIT Bombay. I want to discuss my experience
for the position advertised for the research fellow in computation. I found the current job opening
through the job portal site on the NUS university's official website.\\

%narrate why you want to apply
\vspace{1em} As part of my Ph.D., I have developed a numerical technique in
smoothed particle hydrodynamics to study fluid and elastic dynamics (SPH). Further,
the developed method is coupled with the discrete element method (DEM) to handle the
rigid-fluid coupling, where ocean engineering problems are handled.
Specifically, a new contact force model is used to model the interaction between
arbitrarily shaped bodies. As a multiphysics application, the developed
technique is applied to model the fluid-structure interaction phenomenon. All
the above work is implemented in PySPH and is fully open-source and
reproducible. I have developed a parallel n-body software in memory-safe Rust
programming language, in which DEM is implemented.\\

\vspace{1em}
In addition to the multiphase modeling, I have modeled the collision of elastic
solids by modeling the contacts with DEM in SPH. I have also worked in the area
of elastic-plastic modeling, where I have studied the erosion of plastic targets
due to rigid bodies' impact. In addition to these, I am comfortable with
object-oriented programming in Python and have worked in Linux operating systems
through out my Ph.D. tenure.\\


\vspace{1em}
With my demonstrated experience with working in the intersection of ocean
engineering and multiphase problems, I believe that I am eligible for the proposed
position. I am sure that my proven ability to work on the proposed project will
be of utmost benefit to the institution and can make a significant
contribution to the group.\\


\vspace{1em}
Because my resume only summarizes my background, I would welcome the opportunity
to meet with you to discuss the project interests. Thanks for your
consideration, and I look forward to hearing from you soon.\\

% Sincerely,


\vspace{0.5cm}


\makeletterclosing

\end{document}
