%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Dinesh}{Adepu}
\email{adepu.dinesh.a@gmail.com}
\phone[mobile]{+91 9963943672}
\address{11-29-106, 2nd Bank Colony, Warangal, India}


\begin{document}

\recipient{To}{The Project Incharge, \\
               Lund University,\\
               Sweden}
\date{\today}
\opening{\textbf{Sub: Application for the post of Postdoctoral position in Turbomachinery Aerodynamics.}}
% with reference advertisement: XXXX/XX, dated 04-03-2022
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear sir,
\\
%references such as what and how you got this information
\vspace{1em}
I am Dinesh Adepu, and I hold an M.Tech and Ph.D. in Aerospace
Engineering from IIT Bombay, followed by a postdoctoral fellowship in
the Chemical Engineering Department at the University of
Surrey. Currently, I am working as a postdoctoral researcher at IIT
Delhi, India. \\


\vspace{1em}
During my Ph.D., I developed a novel numerical technique in Smoothed
Particle Hydrodynamics (SPH) to study fluid and elastic dynamics.
Further, the developed method is coupled with the discrete element
method (DEM) to handle the rigid-fluid coupling, where ocean
engineering problems are handled. As a multiphysics application, the
developed technique is applied to model the fluid-structure
interaction phenomenon.  As a postdoctoral researcher at the
University of Surrey, I contributed to an EPSRC-funded project
studying particle dispersion, swelling, and agglomeration in stirring
tanks using an SPH-DEM solver.\\

\vspace{1em}
All the above work is implemented in PySPH and is fully open-source
and reproducible. I have developed a parallel n-body software in
memory-safe Rust programming language, in which DEM is implemented.
To address large-scale mixing challenges, I also created an
exascale-capable DEM solver using the Cabana framework, built on C++
and leveraging Kokkos for heterogeneous computing. \\



\vspace{1em}
With my demonstrated experience in addressing multiphase problems,
CFD, large scale code development I believe I am well-qualified for
the proposed position. I am confident that my proven ability to tackle
the new challenge of addressing turbomachinery aerodynamics using my
proior experience will bring significant value to the institution and
contribute meaningfully to the success of the project.\\



\vspace{1em}
Thank you for considering my application. I look forward to the
opportunity to discuss my qualifications further.\\

% Sincerely,


\vspace{0.5cm}


\makeletterclosing

\end{document}
