%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Dinesh}{Adepu}
\email{adepu.dinesh.a@gmail.com}
\phone[mobile]{+91 9963943672}
\address{11-29-106, 2nd Bank Colony, Warangal, India}


\begin{document}

\recipient{To}{The HR, \\
               Siemens Software,\\
               Pune, India}
\date{\today}
\opening{\textbf{Sub: Application for the post of Discrete Phase Model Developer.}}
% with reference advertisement: XXXX/XX, dated 04-03-2022
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear Madam/Sir,
\\
%references such as what and how you got this information
\vspace{1em} I am Dinesh Adepu, currently working as a postdoctoral in the
school of chemistry and chemical engineering at the university of Surrey.  I
want to discuss my experience for the position advertised for the discrete phase
model developer position. \\

%narrate why you want to apply
\vspace{1em} As part of my Ph.D., I have developed a numerical technique in
smoothed particle hydrodynamics to study fluid and elastic dynamics (SPH). Further,
the developed method is coupled with the discrete element method (DEM) to handle the
rigid-fluid coupling, where ocean engineering problems are handled.
Specifically, a new contact force model is used to model the interaction between
arbitrarily shaped bodies. As a multiphysics application, the developed
technique is applied to model the fluid-structure interaction phenomenon. All
the above work is implemented in PySPH and is fully open-source and
reproducible. I have developed a parallel n-body software in memory-safe Rust
programming language, in which DEM is implemented.\\

\vspace{1em}
In addition to the multiphase modeling, I have modeled the collision of elastic
solids by modeling the contacts with DEM in SPH. I have also worked in the area
of elastic-plastic modeling, where I have studied the erosion of plastic targets
due to rigid bodies' impact. In addition to these, I am comfortable with
object-oriented programming in Python and have worked in Linux operating systems
through out my Ph.D. tenure.\\


%narrate why you want to apply
\vspace{1em} I'm presently engaged in postdoctoral research focusing on studying
particle dispersion and mixing behavior within stirring tanks. My work involves
utilizing the coupled Smoothed Particle Hydrodynamics (SPH) - Discrete Element
Method (DEM) model. To facilitate this study, I'm developing both the DEM and
SPH solvers within the Cabana particle library. This library is specifically
designed to operate efficiently across various computing architectures,
including GPU and CPU, supporting both serial and parallel computations, which
is developed at Argonne national laboratory and many other US laboratories.  In
addition to the base model, I'm introducing cohesion among the particles to
investigate the mixing properties of powders under different stirring
speeds. This cohesive element enhances our understanding of the mixing dynamics
within the system. \\


\vspace{1em} With my demonstrated experience with the code development of
discrete element method, SPH and coupled physics, I believe that I am eligible
for the proposed position. I am sure that my proven ability to work on the
proposed position will be of utmost benefit to the company and can make a
significant.\\


\vspace{1em}
Because my resume only summarizes my background, I would welcome the opportunity
to meet with you to discuss the project interests. Thanks for your
consideration, and I look forward to hearing from you soon.\\

% Sincerely,


\vspace{0.5cm}


\makeletterclosing

\end{document}
