%Author by Rajib Das Bhagat (rajibdasbhagat@gmail.com)
%
\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[english]{babel}

\moderncvstyle{classic}
\moderncvcolor{black}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Dinesh}{Adepu}
\email{adepu.dinesh.a@gmail.com}
\phone[mobile]{+91 9963943672}
\address{11-29-106, 2nd Bank Colony, Warangal, India}


\begin{document}

\recipient{To}{Prof. Yansong Shen, \\
               UNSW Sydney,\\
               Austrailia}
\date{\today}
\opening{\textbf{Sub: Application for Postdoctoral Fellow in Blast Furnace Modelling, CFD-DEM.}}
% with reference advertisement: XXXX/XX, dated 04-03-2022
\closing{Your Sincerly, \vspace{-1em}}


% \enclosure[Enclosed (Marksheets/Certificates)]{
%               \\ 1. SSLC (Admit/MarkSheet/Certificate)
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
%                  }
\makelettertitle



Dear Sir,
\\
%references such as what and how you got this information

\vspace{0.5cm}
I am Dinesh Adepu, and I have completed an M.Tech and
Ph.D. program in Aerospace Engineering at IIT Bombay, followed by a postdoctoral
fellowship in the Chemical Engineering Department at the University of Surrey. I
am interested in discussing my experience in relation to the postdoctoral fellow
position currently advertised.


\vspace{0.5cm}
During my Ph.D., I developed a numerical technique in smoothed particle
hydrodynamics (SPH) to study fluid and elastic dynamics. This method was further
enhanced by coupling it with the discrete element method (DEM) to address
rigid-fluid coupling problems, incorporating a novel contact force model to
simulate interactions between arbitrarily shaped bodies. As a multiphysics
application, the technique was applied to model fluid-structure interaction,
rigid-fluid coupling, solid-body erosion phenomena. All the work was implemented
in PySPH and is fully open-source and reproducible. I also developed parallel
n-body software using the memory-safe Rust programming language, implementing
DEM within this framework. Additionally, I am proficient in object-oriented
programming and have extensive experience working with Linux operating systems
throughout my Ph.D. tenure.


\vspace{0.5cm}
During my postdoctoral work at the University of Surrey, I was
involved in an EPSRC-funded project where I studied particle dispersion,
swelling, and agglomeration in stirring tanks using an SPH-DEM solver. An
open-source solver was developed as part of this project, implemented within
PySPH, with DEM incorporated into the framework
(\href{https://github.com/dineshadepu/sph\_dem}{link}). To address large-scale
mixing challenges, I also developed an exascale-capable DEM solver using the
Cabana framework, which is built on C++ and leverages Kokkos for heterogeneous
computing (\href{https://github.com/ExaPhysics/CabanaDEM}{link}).


\vspace{0.5cm}
With my demonstrated experience in developing numerical techniques for both
continuum and discrete media and applying them across various domains, I am
confident in my eligibility for the proposed position. I am certain that my
expertise and proven ability to work on related projects will be highly
beneficial to the institution and will allow me to make a significant
contribution to the research group.


\vspace{0.5cm}
Because my resume only summarizes my background, I would welcome the opportunity
to meet with you to discuss the project interests. Thanks for your
consideration, and I look forward to hearing from you soon.



\makeletterclosing

\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
