% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/awesome-latex-cv
%
% Author:
% Junhao Hua


%Section: Work Experience at the top
\sectionTitle{Projects}{\faCode}
\begin{experiences}
  \experience
  {} {A DEM solver in Cabana (An exascale capable heterogenous computing particle library)}{}{}
  {}    {
    \begin{itemize}
    \item Implemented the Discrete Element Method (DEM) within the Cabana
      particle library, designed to operate efficiently on both GPU and CPU
      architectures, supporting serial and parallel computations.
    \item Non-linear contact force model is employed.
      \faGithub: \link{https://github.com/ExaPhysics/CabanaDEM}{https://github.com/ExaPhysics/CabanaDEM},
    \end{itemize}
  }
  {N-body, Cabana, Kokkos, C++, HPC, DEM, Heterogeneous computing}

  \emptySeparator
  \experience
  {} {A rigid body solver in Cabana (An exascale capable heterogenous computing particle library)}{}{}
  {}    {
    \begin{itemize}
    \item Implemented the 3D-rigid body dynamics sovler within the Cabana
      particle library, designed to operate efficiently on both GPU and CPU
      architectures, supporting serial and parallel computations.
      \faGithub: \link{https://github.com/ExaPhysics/CabanaRigidBody}{https://github.com/ExaPhysics/CabanaRigidBody},
    \end{itemize}
  }
  {N-body, HPC, DEM, SPH}

  \emptySeparator
  \experience
  {} {An SPH-DEM solver in PySPH}{}{}
  {}    {
    \begin{itemize}
    \item Implemented the Discrete Element Method (DEM) within the PySPH
      particle library, designed to run CPU architectures, supporting serial and
      parallel computations.
    \item Adapting it to run simulations of hydrocolloids mixing in stirring
      tanks at industry scale.
    \item Cohesion among the solid particles is implemented using DMT model.
    \item Particle swelling due to water absorption is implemented.
      \faGithub: \link{https://github.com/dineshadepu/sph\_dem}{https://github.com/dineshadepu/sph\_dem},
    \end{itemize}
  }
  {N-body, HPC, DEM, SPH}

  \emptySeparator
  \experience
    {}   {A corrected transport-velocity formulation for fluid and structural mechanics with SPH}{}{}
    {} {
                      \begin{itemize}
                      \item Developed a corrected transport velocity formulation in SPH to model
                        fluid and elastic dynamics.
                      \item The solver is developed in PySPH % (link{https://github.com/pypr/pysph}{PySPH})
                      \item Fully reproducible and open source. (\link{https://gitlab.com/pypr/ctvf}{Code link})
                      \item \faGithub: \link{https://gitlab.com/pypr/ctvf}{https://gitlab.com/pypr/ctvf}
                      \end{itemize}
                    }
                    {PySPH, SPH, Freesurfaceproblems, Python}
  \emptySeparator
  \experience
  {} {Rigid fluid coupling}{}{}
  {}    {
                    \begin{itemize}
                    \item Developed a SPH-DEM solver in PySPH software.
                    \item The DEM solver can handle interaction between the arbitrarily shaped bodies.
                    \item Studied transport of bodies under a dam-breaking event.
                    \end{itemize}
                  }
                  {Arbitrarily shaped rigid bodies, Rigid-fluid coupling, Discrete element method, SPH, CTVF}

  \emptySeparator
  \experience
  {} {Fluid structure interaction}{}{}
  {}    {
    \begin{itemize}
        \item Implemented a total Lagrangian framework for fluid structure interaction in SPH.
        \item FSI problems involving free surfaces are solved.
        \item Fully reproducible using Automan package.
    \end{itemize}
  }
  {Fluid-structure interaction (FSI), SPH, CTVF}
  \emptySeparator
  \experience
  {} {Elastic bodies collision with SPH-DEM coupling}{}{}
  {} {
                      \begin{itemize}
                      \item  A contact force model incorporated into an updated-Lagrangian SPH is developed.
                      \item  Unphysical interaction of the elastic solids within the classical SPH is eliminated.
                      \item  The method can easily handle friction between two solids.
                      \item  The source code is made available under an open source license.
                        \faGithub: \link{https://gitlab.com/pypr/csph} {https://gitlab.com/pypr/csph}
                      \end{itemize}
                    }
                    {SPH, DEM, Elastic solids collision, Arbitrarily shaped solids}
  \emptySeparator
  \experience
  {} {A parallel N-body software in Rust (runs on the GPU)}{}{}
  {}    {
    \begin{itemize}
      \item A parallel n-body software in memory safe Rust language.
      \item Accelerated on GPU
      \item Applied to model soil modeling with Discrete element method.
        \faGithub: \link{https://github.com/dineshadepu/prestige_old}{https://github.com/dineshadepu/prestige\_old},
    \end{itemize}
  }
  {N-body, Rust, GPU, High performance computing, Entity-component-system (ECS), Discrete element method}

  \emptySeparator
  \experience
  {} {Dendrite formation in FEniCSx}{}{}
  {}    {
    \begin{itemize}
    \item Numerical Dendrite growth in Li-ion batterismodeling
    \end{itemize}
  }
  {FEM, dendrite, FEniCSx}

  \emptySeparator
  \experience
  {} {GPU-based 3D bioprinting in Rust}{}{}
  {}    {
    \begin{itemize}
    \item Developed a GPU-based particle solver for modeling cell transport in acoustic fields.
    \item Implemented and optimized point-in-cell finder algorithms for efficient particle localization and neighborhood queries on parallel architectures.
    \item Coupled the particle solver with a GPU-based Finite Volume Method (FVM) fluid solver for multiphysics simulations.
    \item Simulated acoustophoretic cell patterning and dynamics in structured ultrasound fields.
    \item Studied the interaction between acoustic forces, fluid flow, and biological cells during bioprinting processes.
    \item GitHub: \href{https://github.com/dineshadepu/prestige_old}{github.com/dineshadepu/prestige\_old}
    \item GitHub: \href{https://github.com/dineshadepu/jaali/}{github.com/dineshadepu/jaali}
    \end{itemize}
  }
  {GPU computing, Rust, Particle methods, DEM, Point-in-cell finder, Parallel computing, High-performance computing, Bioprinting, Acoustophorosis}
\end{experiences}
