% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/huajh-awesome-latex-cv
%
% Author:
% Junhao Hua


%Section: Publications
\sectionTitle{Journal Publications}{\faLeanpub}

\begin{itemize}
\item \textbf{Dinesh Adepu} and Prabhu Ramachandran. ``A corrected transport-velocity
formulation for fluid and structural mechanics with SPH''. \emph{in: arXiv preprint
arXiv:2106.00756 (2021)}, doi: \link{https://doi.org/10.48550/arXiv.2106.00756}{link}.

\item \textbf{Dinesh Adepu} and Prabhu Ramachandran. ``Improved collision
  handling of elastic solids in SPH using a contact force model''. \emph{in:
    Engineering Archive preprint (Aug. 2022),}, doi: \link{https://doi.org/10.31224/2503}{link}.

\item Prabhu Ramachandran, Aditya Bhosale, Kunal Puri, Pawan Negi, Abhinav Muta,
  \textbf{Adepu Dinesh}, Dileep Menon, Rahul Govind, Suraj Sanka, Amal S.
  Sebastian, Ananyo Sen, Rohan Kaushik, Anshuman Kumar, Vikas Kurapati,
  Mrinalgouda Patil, Deep Tavker, Pankaj Pandey, Chandrashekhar Kaushik, Arkopal
  Dutt, and Arpit Agarwal. 2021. ``PySPH: A Python-based Framework for Smoothed
  Particle Hydrodynamics''. \emph{ACM Trans. Math. Softw. 47, 4, Article 34 (December
  2021), 38 pages} doi: \link{https://doi.org/10.1145/3460773}{link}.
\end{itemize}


%Section: Publications
\sectionTitle{Conference Proceedings}{\faLeanpub}

\begin{itemize}
\item \textbf{Dinesh Adepu} and Prabhu Ramachandran. ``Fluid-Structure
  Interaction with an Updated Lagrangian Smoothed Particle Hydrodynamics''.
  \emph{in: 9th International and 49th National Conference of Fluid Mechanics and Fluid Power (FMFP-2022) (Dec. 2022),}, doi: \link{https://doi.org/10.31224/2602}{link}.
\end{itemize}
