% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/huajh-awesome-latex-cv
%
% Author:
% Junhao Hua

\par{
{\textbf{Bio.}}


I completed my PhD at the Indian Institute of Technology Bombay,
India, in the Department of Aerospace Engineering. During my doctoral
studies, my research focused on the application of mesh-free methods
for solving partial differential equations.

Following my PhD, I worked as an EPSRC Postdoctoral Researcher at the
University of Surrey, Guildford, United Kingdom. My research there
primarily involved the computational investigation of particle
dispersion and mixing in stirred tanks, including phenomena such as
particle dispersion, swelling, and agglomeration.

I then worked as a postdoctoral researcher at IIT Delhi, where my
research focused on second-life batteries, particularly dendrite
formation and capacity degradation.

Currently, I am a postdoctoral researcher at DWI, where I work on
computational modeling of bioprinting processes. My work involves
solving compressible Navier–Stokes equations using the finite volume
method and studying tissue printing through cell acoustophorosis.

Across these roles, I have employed numerical methods such as Smoothed
Particle Hydrodynamics (SPH), the Discrete Element Method (DEM), and
the Finite Element Method (FEM), Finite Volume Method (FVM). I develop
scalable, high-performance computational codes with heterogeneous
architectures, targeting large-scale and exascale systems.


{\textbf{Research interests.}} My research work covers a range of
topics: \textbf{Meshless methods}: Smoothed particle hydrodynamics,
Discrete element method, Finite element method, High-performance
computing, ExaScale computing, Rigid-fluid coupling, Fluid-structure
interaction, Elastic-plastic modeling, Particle dispersion, Cohesive
materials.
